Thermodynamic fragments in magic state theories

### 2020-07-17 magic_paper.tex
Added two figures that illustrate the phi distributions

>>>>

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/Phi.pdf}
    \caption{Distributions $\Phi(m;n,p)$ (blue) and $\Phi^c(m;n,p)$ (orange) for $n=20$ and $p=\frac{4}{5}$.
    The green curve is the upper bound on $\Phi$, valid for all $m \leq np = 8$.
    }
    \label{fig:Phi}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/Phi_ratio.pdf}
    \caption{Distributions $\Phi_+(m;n,p)$ (blue) and $\Phi_-(m;n,p)$ (orange) for $n=20$ and $p=\frac{4}{5}$.
    The green curve is the ratio of the two
    }
    \label{fig:Phi_ratio}
\end{figure}
